**Measuring Depression and Anxiety with 4 items? Adaptation of the PHQ-4 to increase its Sensitivity to Subclinical Variability**

### 2024-12-12 paper/4_WIP/manuscript.qmd
small changes plus caption docs

The short version of the State-Trait Anxiety Inventory [STAI-5, @zsido2020development] was used as a ground truth measure of anxiety. This abridged version of the STAI [@marteau1992development] includes 5 items rated on a 4-point Likert scale. Changes were made in the instructions from asking *"how participants feel right now"* to *"over the past 2 weeks"* to keep it consistent with the instructions of the PHQ-4 and BDI-II. A general score of anxiety was computed by averaging all the items.

>>>>

The short version of the State-Trait Anxiety Inventory [STAI-T5, @zsido2020development] was used as a ground truth measure of anxiety. This abridged version of the STAI [@spielberger1970manual] includes 5 items rated on a 4-point Likert scale. Changes were made in the instructions from asking *"how participants feel right now"* to *"over the past 2 weeks"* to keep it consistent with the instructions of the PHQ-4 and BDI-II. A general score of anxiety was computed by averaging all the items.
